\documentclass[10pt,a4paper]{article}
\newcommand{\taback}{\hspace*{9.5 cm}}
\begin{document}
\begin{center}
\section*{ACKNOWLEDGEMENT \\}
\end{center}
\vspace*{10.3mm}

We would like to express our gratitude to our college Sir M Visvesvaraya Institute of Technology and particularly our Department of Computer science and Engineering for helping us in this endeavour. \\ \\

Our special thanks to Dr M.S Indira, Principal, Sir MVIT, for all the facilities provided. \\ \\

We are also grateful to Prof. Dilip K Sen, Head of the Department, Computer Science and Engineering, Sir MVIT, for his support and encouragement that went a long way in successful completion of this project. \\ \\

Our sincere thanks to our internal guide Mr G.Thippeswamy, Asst.Professor, Department of Computer science and Engineering,Sir MVIT for giving us invaluable suggestions and guidance during the course of the project and all the faculties and non-teaching staff of Department of Computer science and Engineering, Sir MVIT, for helping us directly or indirectly in completing the project. \\ \\ 

We would like to thank our project coordinators Mr. Shreyas Suresh Rao and Mr G.Thippeswamy, Department of Computer science and Engineering, Sir MVIT for the immense support and suggestions.  
Lastly,we would like to thank our family and friends for their encouragement. \\ \\

\begin{table}[h]

\begin{tabular}{lr} \\

\\
Dharini S \taback & 1MV07CS025   \\
Guru Prasad M \taback & 1MV07CS029   \\
Kiran Tej J L  \taback & 1MV07CS043  \\
Kunal Ghosh \taback &  1MV07CS048   \\ 
\end{tabular}
\end{table}

\end{document}


